### 2013-07-22 doc/asplos14/overview.tex
Overview: Reorder DSM and Communication, and put more emphasis on delegation in DSM
(sorry about the bad diff because I moved text)
note: also removed mention of caches here

\item [Tasking system.] The tasking system supports lightweight multithreading
to tolerate communication latency and global distributed work-stealing (i.e.,
tasks can be stolen from any node in the system), which provides automated
load balancing. The scheduler oversubscribes to have more worker threads than
required for latency tolerance. By having at least four workers per processor
core ready to run at all times, the scheduler can prefetch a worker's state
into cache to lower the likelihood of costly main memory accesses during a
context switch.

\item[Distributed shared memory.] The DSM system provides fine-grain access to
data anywhere in the system. It supports normal access operations such as
\emph{read\/} and \emph{write\/} as well as synchronizing operations such as
\emph{fetch-and-add\/}~\cite{fetchandadd}. It also offers explicit local
caching of any memory in the system, and delegates that directly operate on
remote data. The memory model offered is similar to what underpins
C/C++~\cite{N2480,N2800}, so it is familiar to programmers. The DSM system
design relies on the lightweight tasking system and communication layer in
order to offer high aggregate random access bandwidth for accessing remote
data.

@@

>>>>

\item [Tasking system.] The tasking system supports lightweight multithreading
to tolerate communication latency and global distributed work-stealing (i.e.,
tasks can be stolen from any node in the system), which provides automated
load balancing. The scheduler oversubscribes to have more worker threads than
required for latency tolerance. By keeping at least four workers per 
core ready to run at all times, the scheduler can prefetch a worker's state
into cache to reduce the chance of stalling on memory accesses during a
context switch.

@@

\item[Distributed shared memory.] The DSM system provides fine-grain access to
data anywhere in the system, with delegated operation at the core of its design.
Every piece of global memory is owned by a particular core in the system, and all others may only access that memory by delegating their requests to the owning core.
It supports normal access operations such as
\emph{read\/} and \emph{write\/} as well as synchronizing operations such as
\emph{fetch-and-add\/}~\cite{fetchandadd}. Due to delegation, the memory model offered is similar to what underpins
C/C++~\cite{N2480,N2800}, so it is familiar to programmers. The DSM system
design relies on the lightweight tasking system and communication layer in
order to offer high aggregate random access bandwidth for accessing remote
data.
